Temporal Variations In Vapor Intrusion-Induced Indoor Air Contaminant Concentrations

### 2019-04-30 tex/main.tex
Working on more formatting

% additional packages
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{array,multirow,graphicx}
\usepackage{comment}
\graphicspath{
  {./figures/},
}
\usepackage{lineno}
\linenumbers
% macros

@@

\begin{table}[htb!]
 \begin{tabular}{c c c c c c c}
  \toprule
                                     & \multicolumn{2}{c|}{\textbf{North Island}} & \multicolumn{2}{c|}{\textbf{ASU, PP Open}} & \multicolumn{2}{c}{\textbf{ASU, PP Closed}}                      \\
  Percentile                         & 5th                                            & 95th                                            & 5th                                              & 95th & 5th  & 95th \\
  $p_\mathrm{in/out}$ (Pa)           & -19.9                                          & 7.4                                             & -1.4                                             & 2.1  & -2.1 & 2.27 \\
  $c_\mathrm{in}/c_\mathrm{in,mean}$ & 4.1                                            & 0.2                                             & 13.5                                             & 0.2  & 3.3  & 0.4  \\
  \bottomrule
 \end{tabular}
 \caption{5th and 95th percentile values of $p_\mathrm{in/out}$ and $c_\mathrm{in}/c_\mathrm{in,mean}$ in Figure \ref{fig:kde}.}\label{tbl:percentiles}
\end{table}

@@

\begin{table}[htb!]
 \begin{tabular}{l c c c}
  \toprule
  \textbf{Percentile}                                                     & \textbf{10th} & \textbf{50th} & \textbf{90th} \\
  EPA\cite{u.s._epa_exposure_2011,m._d._koontz_estimation_1995}           & 0.16-0.2      & 0.35-0.49     & 1.21-1.49     \\
  ASU house\cite{holton_temporal_2013,guo_identification_2015}            & 0.21          & 0.43          & 0.78          \\
  Indianapolis\cite{u.s._environmental_protection_agency_assessment_2015} & 0.34          & 0.74          & 1.27          \\
  \bottomrule
 \end{tabular}
 \caption{Air exchange rate values (1/hr)}\label{tbl:air_exchange_rate}
\end{table}

@@

@@

% TODO: Fix the natbib issues...
%\bibliographystyle{model1-num-names}
\bibliography{./library.bib}

>>>>

% additional packages
\usepackage[utf8]{inputenc}
%\bibliographystyle{abbrvnat}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{subcaption}
\usepackage{tabularx}
\usepackage{array,multirow,graphicx}
\usepackage{comment}
\graphicspath{
  {./figures/},
}
\usepackage{lineno}
\linenumbers
% macros

@@

\begin{table}[htb!]
  \centering
 \begin{tabular}{c c c c c c c}
  \toprule
                                     & \multicolumn{2}{c|}{\textbf{North Island}} & \multicolumn{2}{c|}{\textbf{ASU, PP Open}} & \multicolumn{2}{c}{\textbf{ASU, PP Closed}}                      \\
  Percentile                         & 5th                                            & 95th                                            & 5th                                              & 95th & 5th  & 95th \\
  $p_\mathrm{in/out}$ (Pa)           & -19.9                                          & 7.4                                             & -1.4                                             & 2.1  & -2.1 & 2.27 \\
  $c_\mathrm{in}/c_\mathrm{in,mean}$ & 4.1                                            & 0.2                                             & 13.5                                             & 0.2  & 3.3  & 0.4  \\
  \bottomrule
 \end{tabular}
 \caption{5th and 95th percentile values of $p_\mathrm{in/out}$ and $c_\mathrm{in}/c_\mathrm{in,mean}$ in Figure \ref{fig:kde}.}\label{tbl:percentiles}
\end{table}

@@

\begin{table}[htb!]
  \centering
 \begin{tabular}{l c c c}
  \toprule
  \textbf{Percentile}                                                     & \textbf{10th} & \textbf{50th} & \textbf{90th} \\
  EPA\cite{u.s._epa_exposure_2011,m._d._koontz_estimation_1995}           & 0.16-0.2      & 0.35-0.49     & 1.21-1.49     \\
  ASU house\cite{holton_temporal_2013,guo_identification_2015}            & 0.21          & 0.43          & 0.78          \\
  Indianapolis\cite{u.s._environmental_protection_agency_assessment_2015} & 0.34          & 0.74          & 1.27          \\
  \bottomrule
 \end{tabular}
 \caption{Air exchange rate values (1/hr)}\label{tbl:air_exchange_rate}
\end{table}

@@

\section{Conclusions}

Based on the statistical analysis of the field data presented, as well as the modeling efforts the following conclusions may be drawn.
\begin{itemize}
  \item Indoor air contaminant concentrations are unlikely to vary by more than a factor of three over a week-long period if the site is not characterized by a preferential pathway, such as the one found at the ASU house site; else more than an order magnitude variability within the same period may be expected.
  \item Preferential pathways can cause significant spatial variability in the subslab. Subsequently, subslab vapor samples may reveal that the attenuation from subslab may significantly exceed the EPA recommended value of 0.03 and even exceed unity - potentially leading to the erroneous conclusion that an indoor source is present.
  \item Preferential pathways such as the one found at the ASU house significantly increase the advective transport potential through the foundation breaches at a site. This relies on effective communication between the indoor air space and the preferential pathway, e.g. a permeable subslab region (gravel layer) must exist.
  \item Sites characterized by significant advective potential, such as North Island NAS or the ASU house with the preferential pathway open, most of the short-term indoor air contaminant concentration variability may be attributed to fluctuations in indoor/outdoor pressure difference; at sites where the advective potential is low, e.g. ASU house with the preferential pathway closed, short-term variability is dominated by fluctuations in air exchange rate.
\end{itemize}

@@

% TODO: Fix the natbib issues...
\bibliographystyle{model1-num-names}
\bibliography{library}
